The Ex-Ante View of Recommender System Design

### 2019-09-16 paper/filter_bubbles.tex
made some sentences red

\usepackage{xspace}
\newcommand{\OMIT}[1]{}
%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

Stacking utilities in vector-form, we get:
\begin{align*}
{\left(u_{in}\right)}_{n \in \mathcal{N}}=:U_i=V_i+ \beta V
\end{align*}
We stack the idiosyncratic and common-value components as $V_i ={\left(v_{in}\right)}_{n \in \mathcal{N}}$ and $V={\left(v_{n}\right)}_{n \in \mathcal{N}}$.
\par
\noindent \textbf{user Beliefs} We assume that users do not know the realized utilities of the goods before consuming an item.  Formally, user $i$ starts with some beliefs about $U_i$, namely that the idiosyncratic and common-value parts of the utilities are independent -- $V_i \perp \!\!\! \perp V$ -- and that each is multivariate normal. The idiosyncratic utility and common-value utility are distributed as follows:
\begin{enumerate}
\item $V_i \sim \mathcal N (\overline V_i, \Sigma_i)$ 
\item $V \sim \mathcal N(\overline V, \Sigma)$ with $\overline V =0$
\end{enumerate}

We impose the normality assumption for two reasons. The first is that users update their beliefs using Bayesian updating and recall that the normal distribution forms a conjugate family, which allows for simple posterior updates. The second is that it allows us to incorporate an easily interpretable correlation structure between the items.

>>>>

\usepackage{color-edits}
\usepackage{xspace}
\newcommand{\OMIT}[1]{}
%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

Stacking utilities in vector-form, we get:
\begin{align*}
{\left(u_{in}\right)}_{n \in \mathcal{N}}=:U_i=V_i+ \beta V
\end{align*}
We stack the idiosyncratic and common-value components as $V_i ={\left(v_{in}\right)}_{n \in \mathcal{N}}$ and $V={\left(v_{n}\right)}_{n \in \mathcal{N}}$.
\par
\noindent \textbf{user Beliefs} We assume that users do not know the realized utilities of the goods before consuming an item.  Formally, user $i$ starts with some beliefs about $U_i$, namely that the idiosyncratic and common-value parts of the utilities are independent -- $V_i \perp \!\!\! \perp V$ -- and that each is multivariate normal. The idiosyncratic utility and common-value utility are distributed as follows:
\begin{enumerate}
\item $V_i \sim \mathcal N (\overline V_i, \Sigma_i)$ 
\item $V \sim \mathcal N(\overline V, \Sigma)$ with \ssedit{$\overline V =0}{red}$
\end{enumerate}

We impose the normality assumption for two reasons. \ssedit{The first is that users update their beliefs using Bayesian updating and recall that the normal distribution forms a conjugate family, which allows for simple posterior updates.}{red} The second is that it allows us to incorporate an easily interpretable correlation structure between the items.
